### 2016-05-23 intro.tex
cheers

Security relative to this notion appears to have some practical relevance.  [NY] points to whitelisting spam filters as an example.  That is, a Bloom filter is populated with set~$S$ of whitelisted email addresses, so a false positive translates to an attacker finding an email address that sneaks through the filter.  [NY] suggest a second example of content-caching servers that keep a Bloom filter of their own storage contents.  A false positive causes the server to search its local store, which is slow, only to find nothing.

@@

I am less critical of the second example, although this is mostly because I feel ignorant of how real CDNs operate.  However, I believe that the following is common.  Say I'm a caching server.  If my Bloom filter tells me that some requested content is not locally stored, then I check the Bloom filters of my network neighbors, these having been shared with me.  When a neighbor's Bloom filter is positive for the requested content, I contact that neighbor, and that neighbor only.  (If no neighbor has it, then I have to retrieve it from some slower and more distant source, like the Web.)  Now, the [NY] construction uses a PRP, meaning that a secret key is involved in evaluating the Bloom filter.  Thus, I need to know the secret keys of my neighbors in order to operate in the way just described.  This seems troublesome in practice, at scale.  Thus, their solution to a (potentially) real problem seems to be a non-solution.

>>>>

Security relative to this notion appears to have some practical relevance.  [NY] points to whitelisting spam filters as an example.  That is, a Bloom filter is populated with set~$S$ of whitelisted email addresses, so a false positive translates to an attacker finding an email address that sneaks through the filter.  [NY] suggest a second example of content-caching servers that keep a Bloom filter of their own storage contents.  A false positive causes the server to search its local store, which is slow, only to find nothing. \tsnote{Question: in their security notions, the adversary wins by returning an $x^*$ that is not in~$S$ and is not one of the queries it asked to $B_2$; why the latter?  I understand why you shouldn't get credit for output something in~$S$ when~$S$ is given to you, but what if one of the queries to~$B_2$ is not in~$S$ and is a FP?  Shouldn't the adversary already win?}

@@

I am less critical of the second example, although this is mostly because I feel ignorant of how real CDNs operate.  However, I believe that the following is common.  Say I'm a caching server.  If my Bloom filter tells me that some requested content is not locally stored, then I check the Bloom filters of my network neighbors, these having been shared with me.  When a neighbor's Bloom filter is positive for the requested content, I contact that neighbor, and that neighbor only.  (If no neighbor has it, then I have to retrieve it from some slower and more distant source, like the Web.)  Now, the [NY] construction uses a PRP, meaning that a secret key is involved in evaluating the Bloom filter.  Thus, I need to know the secret keys of my neighbors in order to operate in the way just described.  This seems troublesome in practice, at CDN-sized scale. (Also in P2P networks, where peers are joining/leaving frequently.)  Thus, their solution to a (potentially) real problem seems to be a non-solution.
